Tables/Graphs for Article

### 2018-01-23 article/draft1.Rnw
edits

All computation was executed under \texttt{R} version 3.4.3.  \hl{Package for KM curve?} To compute predicted survival probabilities using the model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities. \hl{Include reference for data and functions in oshitaR pacakge?}

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & \hl{0} & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & \hl{0} & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & \hl{0} & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics \hl{of final model?}. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|l L{4cm}| c | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
                  & Camera & -0.3199 (0.0476) & \\ 
                  & Electronics & -0.0138 (0.0904)  & \\ 
                  & Game Console & 0.2458 (0.0784)  & \\ 
                  & Home & 0.3368 (0.0697) &  \\ 
                  & Other & -0.1304 (0.0555)  & \\ 
                  & PC & 0.2818 (0.0597) &  \\ 
                  & Tablet & -0.1566 (0.0815)  & \\ 
                  & Vehicle & 0.4056 (0.0695)  & \\ \hline
  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's text contains end punctuation marks} & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user had been a member for less than one day before posting the question} & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model. Continuous predictors fit with restricted cubic splines are not shown.} 
\label{table:coefficients}
\end{table}

@@

The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \hl{= 0}). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device name (e.g. a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to potentially decrease response times. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\subsubsection*{8.2.6 If the question's text contains end punctuation marks}

@@

This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times. \hl{What is an optimal/desirable/good ratio versus bad?}

>>>>

All computation was executed under \texttt{R} version 3.4.3.  Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R. To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package. This function uses the Cox model and a vector of times to compute predicted survival probabilities. Data used for this analysis can be found in the \texttt{oshitar} package. The function \texttt{variable\_setup} of the \texttt{oshitar} package was used to set up all necessary variables in the data.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics of final model (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|l L{4cm}| c | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
                  & Camera & -0.3199 (0.0476) & \\ 
                  & Electronics & -0.0138 (0.0904)  & \\ 
                  & Game Console & 0.2458 (0.0784)  & \\ 
                  & Home & 0.3368 (0.0697) &  \\ 
                  & Other & -0.1304 (0.0555)  & \\ 
                  & PC & 0.2818 (0.0597) &  \\ 
                  & Tablet & -0.1566 (0.0815)  & \\ 
                  & Vehicle & 0.4056 (0.0695)  & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines are not shown)} 
\label{table:coefficients}
\end{table}

@@

The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value <0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device name (e.g. a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to potentially decrease response times. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include additional tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\subsubsection*{8.2.6 If the question's text contains end punctuation}

@@

This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times. Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g. "Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times. Questions with a ratio of greater than 0 tend to have faster response times.
